Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-11-05 revision-1/ygc.tex
Add files via upload

  sharetable(gid, tid, table)
  {   
    v[1, gate: || gid || tid || "1"] := table.v1;
    v[1, gate: || gid || tid || "2"] := table.v2;
    v[1, gate: || gid || tid || "3"] := table.v3;
    v[1, gate: || gid || tid || "4"] := table.v4
  }

  owl(gid) {  { k = flip[2,gate: || gid || .k]; p = flip[2,gate: || gid || .p] }  }
\end{verbatimtab}
}
\end{fpfig}

@@

  evalgate(gid, wva, wvb)  
  {
    let k = keygen(gid,wva.k,wvb.k) in
    let g = gate: || gid in
    let ct = select4(wva.p,wvb.p,
               v[1,g || "tt1"],v[1,g || "tt2"],v[1,g || "tt3"],v[1,g || "tt4"]) in
    let cp = select4(wva.p,wvb.p,
               v[1,g || "pt1"],v[1,g || "pt2"],v[1,g || "pt3"],v[1,g || "pt4"]) in
    { k = k xor ct; p = k xor cp }
  }

@@

  encode(sa, sb)
  {
    let owl1 = owl(sa) in
    let owl2 = owl(sb) in
    v[1,gate: || sa || 1.k] := OT(s[1,sa],owl1.k,(not owl1.k));
    v[1,gate: || sa || 1.p] := OT(s[1,sa],owl1.p,(not owl1.p));
    v[1,gate: || sb || 2.k] := select(s[2,sb],owl2.k,(not owl2.k));
    v[1,gate: || sb || 2.p] := select(s[2,sb],owl2.p,(not owl2.p));
    { wv1 = { k = v[1,gate: || sa || 1.k]; p = v[1,gate: || sa || 1.p] };
      wv2 = { k = v[1,gate: || sb || 2.k]; p = v[1,gate: || sb || 2.p] } }
  }
\end{verbatimtab}
}
\end{fpfig}

>>>>

  sharetable(gid, tid, table)
  {   
    v[1, "gate:" || gid || tid || "1"] := table.v1;
    v[1, "gate:" || gid || tid || "2"] := table.v2;
    v[1, "gate:" || gid || tid || "3"] := table.v3;
    v[1, "gate:" || gid || tid || "4"] := table.v4
  }

  owl(gid) {  { k = flip[2,"gate:" || gid || ".k"]; p = flip[2,"gate:" || gid || ".p"] }  }
\end{verbatimtab}
}
\end{fpfig}

@@

  evalgate(gid, wva, wvb)  
  {
    let k = keygen(gid,wva.k,wvb.k) in
    let g = "gate:" || gid in
    let ct = select4(wva.p,wvb.p,
               v[1,g || "tt1"],v[1,g || "tt2"],v[1,g || "tt3"],v[1,g || "tt4"]) in
    let cp = select4(wva.p,wvb.p,
               v[1,g || "pt1"],v[1,g || "pt2"],v[1,g || "pt3"],v[1,g || "pt4"]) in
    { k = k xor ct; p = k xor cp }
  }

@@

  encode(sa, sb)
  {
    let owl1 = owl(sa) in
    let owl2 = owl(sb) in
    v[1,"gate:" || sa || "1.k"] := OT(s[1,sa],owl1.k,(not owl1.k));
    v[1,"gate:" || sa || "1.p"] := OT(s[1,sa],owl1.p,(not owl1.p));
    v[1,"gate:" || sb || "2.k"] := select(s[2,sb],owl2.k,(not owl2.k));
    v[1,"gate:" || sb || "2.p"] := select(s[2,sb],owl2.p,(not owl2.p));
    { wv1 = { k = v[1,"gate:" || sa || "1.k"]; p = v[1,"gate:" || sa || "1.p"] };
      wv2 = { k = v[1,"gate:" || sb || "2.k"]; p = v[1,"gate:" || sb || "2.p"] } }
  }
\end{verbatimtab}
}
\end{fpfig}
